\Title

### 2016-08-09 manuscript/manuscript.tex
Specify earth radius and correct bottlenecks statement

We also investigated the computation time spent in each section of the inversion
process using a source code profiler.
The profiler measures how much time is spent inside each function during
the execution of a program.
We ran the profiler on a single inversion of the training data set
using the estimated regularization parameter.
We tracked the total time spent inside each of the three functions
that represent the largest computational bottlenecks of the inversion:
solving the linear system in Eq.~\ref{eq:gaussnewton-regul}
using the conjugate gradient method,
performing the dot products required to compute
the Hessian matrix (Eq.~\ref{eq:hessian-regul})
and the gradient vector (Eq.~\ref{eq:gradient-regul}),
and forward modeling to calculate the predicted data (Eq.~\ref{eq:forward}).
The profiling results presented in Table~\ref{profiling}
show that the time spent on forward modeling accounts for approximately
99.8\% of the total computation time.

@@

We apply the inversion method proposed here to invert for the Moho depth of the
South American continent.
We follow the application of \citet{vandermeijde2013} but with some
differences, mainly using a different data set and performing all modeling
in spherical coordinates using tesseroids.
The data are corrected of the effects of topography and sedimentary basins.
Crust and mantle heterogeneities cannot be properly accounted for
in regions where information coverage is sparse and readily accessible models
are not available, like in South America and Africa.
Hence, for the purposes of this study, we will assume to be negligible all
other crustal and mantle sources, including lateral variations in density along
the Moho.

>>>>

We also investigated the computation time spent in each section of the inversion
process using a source code profiler.
The profiler measures how much time is spent inside each function during
the execution of a program.
We ran the profiler on a single inversion of the training data set
using the estimated regularization parameter.
We tracked the total time spent inside each of the three functions
that represent the potential bottlenecks of the inversion:
solving the linear system in Eq.~\ref{eq:gaussnewton-regul}
using the conjugate gradient method,
performing the dot products required to compute
the Hessian matrix (Eq.~\ref{eq:hessian-regul})
and the gradient vector (Eq.~\ref{eq:gradient-regul}),
and forward modeling to calculate the predicted data (Eq.~\ref{eq:forward}).
The profiling results presented in Table~\ref{profiling}
show that the time spent on forward modeling accounts for approximately
99.8\% of the total computation time.

@@

We apply the inversion method proposed here to invert for the Moho depth of the
South American continent.
We follow the application of \citet{vandermeijde2013} but with some
differences, mainly using a different data set and performing all modeling
in spherical coordinates using tesseroids.
The data are corrected of the effects of topography and sedimentary basins.
Crust and mantle heterogeneities cannot be properly accounted for
in regions where information coverage is sparse and readily accessible models
are not available, like in South America and Africa.
Hence, for the purposes of this study, we will assume to be negligible all
other crustal and mantle sources, including lateral variations in density along
the Moho.
All tesseroid models are defined with respect to a spherical Earth of radius
6,378.137 km.
